Predicting the 2024 US Presidential Election with a Model-Based Forecast

### 2024-11-04 paper/paper.qmd
finalize paper

>>>>

```{r}
#| label: tbl-trump-summary
#| tbl-cap: "Summary Statistics of Trump's Support Percentage in 2024 Polling Data"
#| echo: false
#| warning: false

summary_table <- cleaned_data %>%
  summarize(
    Mean = mean(pct, na.rm = TRUE),
    Median = median(pct, na.rm = TRUE),
    Min = min(pct, na.rm = TRUE),
    Max = max(pct, na.rm = TRUE),
    Std_Dev = sd(pct, na.rm = TRUE),
    Count = n()
  )

kable(summary_table,
      col.names = c("Mean", "Median", "Min", "Max", "Standard Deviation", "Count"),
      digits = 2)
```

@tbl-trump-summary presents the key summary statistics for Trump’s support percentage based on a dataset of 348 polling observations from the 2024 U.S. presidential election. The mean support level is 46.47%, indicating that, on average, 46.47% of respondents in the polls expressed support for Trump. The median value of 47% suggests that half of the polls reported support at or below 47%, while the minimum and maximum values show a wide range of support from 27% to 57.9%, reflecting variability across different polls and regions. The standard deviation of 4.73 indicates a moderate spread around the mean, suggesting some diversity in polling results but with a central clustering.
